---
title: "Homework 1"
author: "Samiha Reza"
date: "2024-09-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

usethis::create_github_token()

# Problem 1

Here is the code chunk for ***data description***.

```{r description, echo=TRUE}
data("penguins", package = "palmerpenguins")

summary(penguins)
nrow(penguins)
ncol(penguins)
```

The "penguins" data includes 8 variables: species, island, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex, and year. There are three species: Adelie (152 penguins), Chinstrap (68 penguins), and Gentoo (124 penguins). There are three islands: Biscoe (168 pengiuins), Dream (124 penguins), and Torgersen (52 penguins).
There are 8 columns, and 344 rows, so 344 data samples.The mean flipper length in mm is 200.9. 

Here is the code chunk for the ***scatterplot***

```{r scatterplot}
library(tidyverse)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("penguins_scatter.pdf")
```
# Problem 2

Since we have already loaded tidyverse, we do not need to do it again.
Here we have a code chunk to create the ***data frame***.

```{r dataframe, echo = TRUE}
question_2_df = tibble(
  random_sample = rnorm(10),
  logic_vector = random_sample > 0,
  character_vector = rep("character", 10),
  factor_vector = factor(rep(c("Level1", "Level2", "Level3"), length.out =10)),
)

print(question_2_df)
```
Here we pull variables from the dataframe and try to find the means of each.

```{r variablexplore1}
random_sample <- question_2_df$random_sample
logic_vector <- question_2_df$logic_vector
character_vector <- question_2_df$character_vector
factor_vector <- question_2_df$factor_vector

mean(random_sample)
mean(logic_vector)
mean(character_vector)
mean(factor_vector)
```
Only random_sample and logic_vector has a mean value. Character and Factor vector do not because "argument is not numeric or logical."

We now check if we can convert the variables to numeric ones.

```{r variableexplore1}
numeric_logical = as.numeric(logic_vector)
# numeric_character = as.numeric(character_vector)
# numeric_factor = as.numeric(factor)
```
Character and factor vector cannot be converted to numeric, which is why it isn't possible to find the mean. 


